---
title: "sentiment_by_category"
author: "Huaian Yu"
date: "June 17, 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
full_data <- read.csv("sentiment_df_v1") #from "sentiment_1_v2"
full_data <- na.omit(full_data)
full_data <- full_data[,-1]
library(tidyverse)
library(packcircles)
library(ggplot2)

```

```{r message=FALSE, warning=FALSE, echo = FALSE}
circle_plot <- function(data, title){
  packing <- circleProgressiveLayout(data$new_count, sizetype='area')
  data <- data.frame(data, packing)
  dat.gg <- circleLayoutVertices(packing, npoints=50)
  p = ggplot()
  
  p = p +  geom_polygon(data = dat.gg, aes(x, y, group = id,
                                           fill=as.factor(id)), 
                        colour = "black", alpha = 0.6) +
    geom_text(data = data, aes(x, y, size=new_count, label = value)) +
    scale_size_continuous(range = c(1,4)) +
    theme_void() + 
    theme(legend.position="none") +
    coord_equal() +
    ggtitle(title)
 return(p)
}
```
###0. Introduction
The data is from the Amazon's apparel review data.(For more detailed information: chuck@emadri.com) 

I picked 1000 observations from the full dataset. Then extract adjetives from the "review_body". And judge the category of the product from the "product_tittle". The final dataset contains following variables:  

-product_id: ID of the product being reviewed.

-review_id: The ID of reviewer. 

-attributes: Describes the attributes of the variable "value"

-value: Words extraced from the customer review.

-count: How many time does a single word appears in a single review massage. 

-tf: Term frequency. 

-weight: How rare is the word.

-star_rating: The rating for the product, given by the reviewer.

-item_name: Categories of products.

-category: The category decided by me, for the covience of following analysis. Has 4 values: access(Accessories), top, bot and under(Underwear) (For more info: andy@emadri.com) . 

```{r echo = FALSE}
head(full_data, 10)
```

The purpose of this first step analysis, is to find a set of keywords that are associated with possitive review. Then, to see if these key words could show some insight about how could a customer satisfy with his/her purchase. 

Here, I divide extracted into two groups: possitive and negative. Posstive words are from reviews rated with more than 3 stars. Negative words are from review rated with less than 3 stars. 

In the following plots, words with larger circle means they are more frequently appeared in the review.


###1. Accessories 
```{r message=FALSE, warning=FALSE, echo = FALSE}
access_df <- full_data[which(full_data$category == "access"),]
access_df %>% 
  filter(star_rating > 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> pos_access
pos_access <- pos_access[!duplicated(pos_access$value),]

access_df %>% 
  filter(star_rating < 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> neg_access
neg_access <- neg_access[!duplicated(neg_access$value),]
```

```{r message=FALSE, warning=FALSE, echo = FALSE, dpi = 300}
circle_plot(pos_access, "Postive Words in the Review of Accessories")
circle_plot(neg_access, "Negative Words in the Review of Accessories")
```

###2. Bottom
```{r message=FALSE, warning=FALSE, echo = FALSE}
bot_df <- full_data[which(full_data$category == "bot"),]
bot_df %>% 
  filter(star_rating > 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> pos_bot
pos_bot <- pos_bot[!duplicated(pos_bot$value),]

bot_df %>% 
  filter(star_rating < 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> neg_bot
neg_bot <- neg_bot[!duplicated(neg_bot$value),]
```

```{r message=FALSE, warning=FALSE, echo = FALSE, dpi = 300}
circle_plot(pos_bot, "Postive Words in the Review of Bottom")
circle_plot(neg_bot, "Negative Words in the Review of Bottom")
```

###3. Top
```{r message=FALSE, warning=FALSE, echo = FALSE}
top_df <- full_data[which(full_data$category == "top"),]
top_df %>% 
  filter(star_rating > 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> pos_top
pos_top <- pos_top[!duplicated(pos_top$value),]

top_df %>% 
  filter(star_rating < 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> neg_top
neg_top <- neg_top[!duplicated(neg_top$value),]


```

```{r message=FALSE, warning=FALSE, echo = FALSE, dpi = 300}
circle_plot(pos_top, "Postive Words in the Review of Top")
circle_plot(neg_top, "Negative Words in the Review of Top")
```

###4. Underwear
```{r message=FALSE, warning=FALSE, echo = FALSE}
under_df <- full_data[which(full_data$category == "under"),]
under_df %>% 
  filter(star_rating > 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> pos_under
pos_under <- pos_under[!duplicated(pos_under$value),]

under_df %>% 
  filter(star_rating < 3) %>% 
  group_by(value) %>%
  mutate(new_count = sum(count)) %>% 
  select(value,new_count) -> neg_under
neg_under <- neg_under[!duplicated(neg_under$value),]

```

```{r message=FALSE, warning=FALSE, echo = FALSE, dpi = 300}
circle_plot(pos_under, "Postive Words in the Review of Underwear")
circle_plot(neg_under, "Negative Words in the Review of Underwear")
```

#5. Summary

In general, there are 3 perspectives that affact the review of a product:

1. How does the product look like:

Example words: unique, beautiful, perfect, great, excellent, good, hot, nice, cute, awesome, fashionable, chic

2. How's it feel to wear the product on:

Example words: not heavy, soft, comfortable, adjustable, not too tight, not too large, stretchy, comfy, breathable

3. How's the service offered by the seller:

Example words: unbiased(description on the size/color of the product), honest, real, happy, promotional

```{r message=FALSE, warning=FALSE, echo = FALSE}
top10_access <- (pos_access[order(pos_access$new_count, decreasing = TRUE),])$value
top10_access <- head(top10_access, 10)

top10_bot <- (pos_bot[order(pos_bot$new_count, decreasing = TRUE),])$value
top10_bot <- head(top10_bot, 10)

top10_top <- (pos_top[order(pos_top$new_count, decreasing = TRUE),])$value
top10_top <- head(top10_top, 10)

top10_under <- (pos_under[order(pos_under$new_count, decreasing = TRUE),])$value
top10_under <- head(top10_under, 10)

df_sum <- data.frame(top10_access, top10_bot, top10_top, top10_under)
inter1 <- intersect(top10_access, top10_bot)
inter2 <- intersect(top10_top, top10_under)
inter3 <- intersect(inter1, inter2)
```


